Considering scale in multilayer animal social networks

### 2020-06-23 paper/manuscript.Rmd
temp p

<!-- mov -->
Social processes, movement decisions, and space use are inextricably linked and
multilayer networks represent a potential analytical framework for linking these
processes [@Mourier_2019]. Collective movement can reduce per capita predation
risk via detection-dilution trade-offs and improve information transfer about
the quality or location of resources [@Jolles_2019]. Multilayer networks could
be constructed from layers defined by movement parameters, given the existing
framework using behavioural layers [e.g. @Smith_Aguilar_2019]. For example,
edges could represent measures of collective movement based on dynamic
interaction metrics [@Long_2014]. We generated multilayer networks based on
habitat-specific layers of social association. Integrating habitat-specific
movement layers could further illuminate the role of movement as a driver of the
social and spatial environments an individual experiences [@Webber_2018]. For
example, social processes may be an emergent property of the landscape because
animals aggregate at resources, such as waterholes [@Chamaill_Jammes_2008].
Movement to, from, or within habitat patches or territories can also contribute
to the formation of the social environment [@Spiegel_2016]. For example, in
sleepy lizards (*Tiliqua rugosa*) males interacted primarily at home range
edges, presumably driving territorial behaviour [@Spiegel_2018]. Incorporating
movement ecology within a multilayer network framework is a logical next step
for a burgeoning field. Importantly, the technological advancements in
biologging and wildlife tracking technology [@Border_2020] have provided a
unique opportunity to integrate movement and habitat in multilayer networks to
answer complex questions about animal socioecology.
<!-- mov -->

<!-- temp -->
The effect of seasonality of resources on sociality can be directly measured by
differences across discrete time windows. Using an ordinal multilayer network
consisting of 20 discrete time windows throughout the study period, we observed
periods of increased sociality in caribou on Fogo Island (Figure \@ref(fig:temp)). 
Edge overlap was higher between approximately October and May
(time windows 1, 6-11, 15-20) compared to between approximately May and October
(time windows 2-5, 12-15) (Figure \@ref(fig:temp) A). These periods of high edge
overlap correspond to seasons of heterogeneous resource availability [Peigner_2019].
Similarly, individual graph strength was also highest in these periods (Figure
\@ref(fig:temp) B). By explicitly considering the temporal context of social interactions
in separate layers, multilayer networks provide a detailed and dynamic perspective of
animal social networks.

TODO: add t bonnell
TODO: add autocorrelation

>>>>

<!-- mov -->
Social processes, movement decisions, and space use are inextricably linked and
multilayer networks represent a potential analytical framework for linking these
processes [@Mourier_2019]. Collective movement can reduce per capita predation
risk via detection-dilution trade-offs and improve information transfer about
the quality or location of resources [@Jolles_2019]. Multilayer networks could
be constructed from layers defined by movement parameters, given the existing
framework using behavioural layers [e.g. @Smith_Aguilar_2019]. For example,
edges could represent measures of collective movement based on dynamic
interaction metrics [@Long_2014]. We generated multilayer networks based on
habitat-specific layers of social association. Integrating habitat-specific
movement layers could further illuminate the role of movement as a driver of the
social and spatial environments an individual experiences [@Webber_2018]. For
example, social processes may be an emergent property of the landscape because
animals aggregate at resources, such as waterholes [@Chamaill_Jammes_2008].
Movement to, from, or within habitat patches or territories can also contribute
to the formation of the social environment [@Spiegel_2016]. For example, in
sleepy lizards (*Tiliqua rugosa*) males interacted primarily at home range
edges, presumably driving territorial behaviour [@Spiegel_2018]. Incorporating
movement ecology within a multilayer network framework is a logical next step
for a burgeoning field. Importantly, the technological advancements in
biologging and wildlife tracking technology [@Border_2020] have enabled this
unique opportunity to integrate movement and habitat in multilayer networks to
answer complex questions about animal socioecology.
<!-- mov -->

<!-- temp -->
Changes in network metrics through time can explain the influence of seasonality
of resources on animal sociality. Using an ordinal multilayer network composed
of 20 discrete time windows throughout the study period, we observed periods of
increased sociality in caribou on Fogo Island. Edge overlap was higher during
fall, winter and spring (approximately October - June) than in summer
(approximately June - October)  (Figure \@ref(fig:temp) A). Similarly,
individual graph strength was also highest in these periods (Figure
\@ref(fig:temp) C). Periods of increased sociality correspond to seasons of
heterogeneous resource availability [Peigner_2019]. By explicitly considering
the temporal context of social interactions in separate layers, multilayer
networks provide a detailed and dynamic perspective of animal social networks.
In addition, this could be extended using time-aggregated networks and a moving-window
approach to inform the temporal scale including time window size and sampling effort
[@Farine_2017; @Bonnell_2020].

Due to the autocorrelated nature of biologging data that we recommend users ensure social association data are non-randomly distributed [@Farine_2017b].
